---
title: "2026-7 Events"
execute: 
  echo: false
editor: visual
editor_options: 
  chunk_output_type: inline
---

```{r, setup, include=FALSE}
library(knitr)
library(rmarkdown)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 5)
library(tidyverse)
library(here)
library(english)
source(here("functions", "utility_functions.R"))
```

## Results

The following events are scheduled for the 2026-7 season. For more information about each event, broken down by club, bowstyle, and sex, click on the 'Detailed results' link.

### Stage 1

```{r}
eventDate <- ymd(20261018)
scores <- load_archer_scores(eventDate)
current_venue <- venue(eventDate)
venue_name <- if (nrow(current_venue) > 0) current_venue$location else "Eastwood High School"
if (nrow(scores) > 0) {
  knitr::kable(team_results(scores), col.names = c("Club", "Score", "Hits", "Golds"))
}
```

*Venue:* `{r} venue_name`. *Date:* 2026-10-18. *Time:* 09:00 - 13:00

[Detailed results](oct26.qmd)

### Stage 2

```{r}
eventDate <- ymd(20261122)
scores <- load_archer_scores(eventDate)
current_venue <- venue(eventDate)
venue_name <- if (nrow(current_venue) > 0) current_venue$location else "The Time Capsule"
if (nrow(scores) > 0) {
  knitr::kable(team_results(scores), col.names = c("Club", "Score", "Hits", "Golds"))
}
```

*Venue:* `{r} venue_name`. *Date:* 2026-11-22. *Time:* 12:30 - 16:30

[Detailed results](nov26.qmd)

### Stage 3

*Venue:* TBC. *Date:* TBC. *Time:* TBC

[Detailed results](dec26.qmd)

### Stage 4

```{r}
eventDate <- ymd(20270124)
scores <- load_archer_scores(eventDate)
current_venue <- venue(eventDate)
venue_name <- if (nrow(current_venue) > 0) current_venue$location else "The Time Capsule"
if (nrow(scores) > 0) {
  knitr::kable(team_results(scores), col.names = c("Club", "Score", "Hits", "Golds"))
}
```

*Venue:* `{r} venue_name`. *Date:* 2027-01-24. *Time:* 12:30 - 16:30

[Detailed results](jan27.qmd)

### Stage 5

```{r}
eventDate <- ymd(20270221)
scores <- load_archer_scores(eventDate)
current_venue <- venue(eventDate)
venue_name <- if (nrow(current_venue) > 0) current_venue$location else "The Time Capsule"
if (nrow(scores) > 0) {
  knitr::kable(team_results(scores), col.names = c("Club", "Score", "Hits", "Golds"))
}
```

*Venue:* `{r} venue_name`. *Date:* 2027-02-21. *Time:* 12:30 - 16:30

[Detailed results](feb27.qmd)

### Stage 6

```{r}
eventDate <- ymd(20270321)
scores <- load_archer_scores(eventDate)
current_venue <- venue(eventDate)
venue_name <- if (nrow(current_venue) > 0) current_venue$location else "The Time Capsule"
if (nrow(scores) > 0) {
  knitr::kable(team_results(scores), col.names = c("Club", "Score", "Hits", "Golds"))
}
```

*Venue:* `{r} venue_name`. *Date:* 2027-03-21. *Time:* 12:30 - 16:30

[Detailed results](mar27.qmd)

## Progress charts

### How do clubs compare in the range of scores?

It can be interesting to see how variable the archers in a particular club are, so these two plots show everyone's scores from all of the events so far. We can also see which clubs seem to favour barebow, compound, or recurve.

```{r}
#| results: asis
season_scores <- load_all_archer_scores() |>
  filter(score > 0, between(event_date, as.Date('2026-10-01'), as.Date('2027-03-31')))

if (nrow(season_scores) > 0) {
  p1 <- ggplot(data = season_scores, aes(x = club, y = score, color = bowstyle)) +
    geom_point() +
    labs(title = "Scores per bow style for each club",
         subtitle = "Combined across all events")
  print(p1)
  
  p2 <- ggplot(data = season_scores, aes(x = club, y = score)) +
    geom_boxplot() +
    labs(title = "Boxplot showing ranges",
         subtitle = "All bowstyles combined")
  print(p2)
} else {
  cat("*Progress charts will appear once event scores are recorded.*")
}
```
