---
title: "February 2027 Tournament"
date: "2027-02-21"
execute: 
  echo: false
editor: visual
editor_options: 
  chunk_output_type: inline
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 5)
library(tidyverse)
library(here)
library(english)
source(here("functions", "utility_functions.R"))
```

```{r}
event_date <- ymd(20270221)
scores <- load_archer_scores(event_date)
current_venue <- venue(event_date)

venue_name <- if (nrow(current_venue) > 0) current_venue$location else "The Time Capsule"
town <- if (nrow(current_venue) > 0) current_venue$town else "Coatbridge"
w3w <- if (nrow(current_venue) > 0) current_venue$w3w else "hoping.gloves.shins"
postcode <- if (nrow(current_venue) > 0) current_venue$postcode else "ML5 1DL"
has_scores <- nrow(scores) > 0
num_teams <- if (has_scores) n_distinct(scores$club) else 0
```

*Venue:* `{r} venue_name`, `{r} town`

*what3words:* `{r} w3w`, *postcode:* `{r} postcode`

*Date:* `{r} event_date`

`{r} if (has_scores) paste(str_to_title(as.english(num_teams)), "teams took part. The scores of the top four members of each team were summed.") else "Scores have not yet been recorded for this event."`

# Team Results

```{r}
#| results: asis
if (has_scores) {
  knitr::kable(team_results(scores), col.names = c("Club", "Score", "Hits", "Golds"))
} else {
  cat("*Scores will be posted following the tournament.*")
}
```

# Individual Scores - by Bowstyle

### Ladies Recurve

```{r}
#| results: asis
if (has_scores) {
  lady_r <- score_table('Recurve', 'Ladies', scores)
  if (nrow(lady_r) > 0) knitr::kable(lady_r, col.names = c("Archer", "Club", "Score", "Hits", "Golds", "Badge"))
} else {
  cat("*No scores yet.*")
}
```

### Ladies Barebow

```{r}
#| results: asis
if (has_scores) {
  lady_b <- score_table('Barebow', 'Ladies', scores)
  if (nrow(lady_b) > 0) knitr::kable(lady_b, col.names = c("Archer", "Club", "Score", "Hits", "Golds", "Badge"))
} else {
  cat("*No scores yet.*")
}
```

### Ladies Traditional

```{r}
#| results: asis
if (has_scores) {
  lady_t <- score_table('Traditional', 'Ladies', scores)
  if (nrow(lady_t) > 0) knitr::kable(lady_t, col.names = c("Archer", "Club", "Score", "Hits", "Golds", "Badge"))
} else {
  cat("*No scores yet.*")
}
```

### Gents Compound

```{r}
#| results: asis
if (has_scores) {
  gent_c <- score_table('Compound', 'Gents', scores)
  if (nrow(gent_c) > 0) knitr::kable(gent_c, col.names = c("Archer", "Club", "Score", "Hits", "Golds", "Badge"))
} else {
  cat("*No scores yet.*")
}
```

### Gents Recurve

```{r}
#| results: asis
if (has_scores) {
  gent_r <- score_table('Recurve', 'Gents', scores)
  if (nrow(gent_r) > 0) knitr::kable(gent_r, col.names = c("Archer", "Club", "Score", "Hits", "Golds", "Badge"))
} else {
  cat("*No scores yet.*")
}
```

### Gents Barebow

```{r}
#| results: asis
if (has_scores) {
  gent_b <- score_table('Barebow', 'Gents', scores)
  if (nrow(gent_b) > 0) knitr::kable(gent_b, col.names = c("Archer", "Club", "Score", "Hits", "Golds", "Badge"))
} else {
  cat("*No scores yet.*")
}
```

### Gents Longbow

```{r}
#| results: asis
if (has_scores) {
  gent_l <- score_table('Longbow', 'Gents', scores)
  if (nrow(gent_l) > 0) knitr::kable(gent_l, col.names = c("Archer", "Club", "Score", "Hits", "Golds", "Badge"))
} else {
  cat("*No scores yet.*")
}
```

### Gents Traditional

```{r}
#| results: asis
if (has_scores) {
  gent_t <- score_table('Traditional', 'Gents', scores)
  if (nrow(gent_t) > 0) knitr::kable(gent_t, col.names = c("Archer", "Club", "Score", "Hits", "Golds", "Badge"))
} else {
  cat("*No scores yet.*")
}
```

# Individual Scores - by Club

::: panel-tabset
## Glasgow

```{r}
#| results: asis
if (has_scores) {
  glas <- club_scores("Glasgow", scores)
  if (nrow(glas) > 0) knitr::kable(glas, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
} else {
  cat("*No scores yet.*")
}
```

## East Kilbride

```{r}
#| results: asis
if (has_scores) {
  ek <- club_scores("East Kilbride", scores)
  if (nrow(ek) > 0) knitr::kable(ek, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
} else {
  cat("*No scores yet.*")
}
```

## Monklands

```{r}
#| results: asis
if (has_scores) {
  monk <- club_scores("Monklands", scores)
  if (nrow(monk) > 0) knitr::kable(monk, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
} else {
  cat("*No scores yet.*")
}
```

## Strathclyde

```{r}
#| results: asis
if (has_scores) {
  strath <- club_scores("Strathclyde", scores)
  if (nrow(strath) > 0) knitr::kable(strath, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
} else {
  cat("*No scores yet.*")
}
```

## Linwood

```{r}
#| results: asis
if (has_scores) {
  lin <- club_scores("Linwood", scores)
  if (nrow(lin) > 0) knitr::kable(lin, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
} else {
  cat("*No scores yet.*")
}
```

## Orion's

```{r}
#| results: asis
if (has_scores) {
  orion <- club_scores("Orion's", scores)
  if (nrow(orion) > 0) knitr::kable(orion, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
} else {
  cat("*No scores yet.*")
}
```
:::
