---
title: "Glasgow (Coatbridge) Tournament"
date: "2025-03-01"
execute: 
  echo: false
editor: visual
editor_options: 
  chunk_output_type: inline
---

```{r, install, eval=FALSE}
install.packages( "quarto", "tidyverse", "here", "english")
```

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 5)
library(tidyverse)
library(here)
library(english)
source(here("functions", "utility_functions.R"))
```

```{r}
event_date = ymd(20250301)
scores <- load_archer_scores(event_date)
current_venue <- venue(event_date)
venue_name <- current_venue$location
town <- current_venue$town
num_teams <- n_distinct(scores$club)
```

*Venue:* `{r} venue_name`, `{r} town`

*Date:* `{r} event_date`

`{r} str_to_title(as.english(num_teams))` teams took part. The scores of the top four members of each time was summed, except Linwood which had one archer on their team.

# Team Results

```{r}
knitr::kable(team_results(scores), col.names = c("Club", "Score", "Hits", "Golds"))
```

# Individual Scores - by Bowstyle

### Ladies Recurve

```{r}
#| warning: false
lady_r <- score_table('Recurve', 'Ladies', scores)
knitr::kable(lady_r, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Compound

```{r}
gent_c <- score_table('Compound', 'Gents', scores)
knitr::kable(gent_c, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Recurve

```{r}
gent_r <- score_table('Recurve', 'Gents', scores)
knitr::kable(gent_r, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Barebow

```{r}
gent_b <- score_table('Barebow', 'Gents', scores)
knitr::kable(gent_b, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### 

# Individual Scores - by Club

::: panel-tabset
## Glasgow

```{r}
glas <- club_scores("Glasgow", scores)
knitr::kable(glas, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## East Kilbride

```{r}
ek <- club_scores("East Kilbride", scores)
knitr::kable(ek, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Monklands

```{r}
monk <- club_scores("Monklands", scores)
knitr::kable(monk, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Strathclyde

```{r}
strath <- club_scores("Strathclyde", scores)
knitr::kable(strath, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Linwood

```{r}
lin <- club_scores("Linwood", scores)
knitr::kable(lin, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Orion's

```{r}
orion <- club_scores("Orion's", scores) 
knitr::kable(orion, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```
:::
