---
title: "Glasgow (Coatbridge) Tournament"
date: "2024-11-24"
execute: 
  echo: false
editor: visual
editor_options: 
  chunk_output_type: inline
---

```{r, install, eval=FALSE}
install.packages("tidyverse", "here", "english")
```

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 5)
library(tidyverse)
library(here)
library(english)
source(here("functions", "utility_functions.R"))
```

```{r}
shoot_date = ymd(20241124)
archer_scores <- load_archers()
venues <- load_venues()
current_venue <- filter(venues, date_of_shoot == shoot_date)
venue_name <- current_venue$venue_name
town <- current_venue$town
num_teams <- n_distinct(archer_scores$club)
event_date <- current_venue$date_of_shoot
scores <- filter(archer_scores, event_date == shoot_date)
```

```{r}
```

*Venue:* `{r} venue_name`, `{r} town`

*Date:* `{r} event_date`

`{r} str_to_title(as.english(num_teams))` teams took part. The scores of the top four members of each time was summed, except Orion which had one archer, and Linwood, which had just three archers on their team.

# Team Results

```{r}
knitr::kable(team_results(scores), col.names = c("Club", "Score", "Hits", "Golds"))
```

# Individual Scores - by Bowstyle

### Ladies Recurve

```{r}
#| warning: false
lady_r <- score_table('Recurve', 'Ladies', scores)
knitr::kable(lady_r, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Ladies Barebow

```{r}
lady_b <- score_table('Barebow', 'Ladies', scores)
knitr::kable(lady_b, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Compound

```{r}
gent_c <- score_table('Compound', 'Gents', scores)
knitr::kable(gent_c, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Recurve

```{r}
gent_r <- score_table('Recurve', 'Gents', scores)
knitr::kable(gent_r, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Barebow

```{r}
gent_b <- score_table('Barebow', 'Gents', scores)
knitr::kable(gent_b, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Longbow

```{r}
gent_l <- score_table('Longbow', 'Gents', scores)
knitr::kable(gent_l, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

# Individual Scores - by Club

::: panel-tabset
## Glasgow

```{r}
glas <- club_scores("Glasgow", scores)
knitr::kable(glas, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## East Kilbride

```{r}
ek <- club_scores("East Kilbride", scores)
knitr::kable(ek, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Monklands

```{r}
monk <- club_scores("Monklands", scores)
knitr::kable(monk, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Strathclyde

```{r}
strath <- club_scores("Strathclyde", scores)
knitr::kable(strath, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Linwood

```{r}
lin <- club_scores("Linwood", scores)
knitr::kable(lin, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Orion's

```{r}
orion <- club_scores("Orion's", scores)
knitr::kable(orion, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```
:::
