---
title: "East Kilbride Tournament"
date: "2024-10-20"
execute: 
  echo: false
editor: visual
editor_options: 
  chunk_output_type: inline
---

```{r, install, eval=FALSE}
install.packages("tidyverse", "here", "english")
```

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 5)
library(tidyverse)
library(here)
library(english)
```

```{r}
score_table <- function(bow, s) {
  tbl <- scores %>%
          filter(bow == bowstyle, sex == s) %>%
          arrange_at(c("score", "golds"), desc) %>%
          select(c("archer", "club", "score", "hits", "golds"))
  
  return(tbl)
}
```

```{r}
shoot_date = ymd(20241020)
archer_scores <- read_csv(here("data", "archer_scores.csv"), col_types = "Dccciiic")
venues <- read_csv(here("data", "venues.csv"), col_type = "Dcccc")
current_venue <- filter(venues, date_of_shoot == shoot_date)
venue_name <- current_venue$venue_name
town <- current_venue$town
num_teams <- n_distinct(archer_scores$club)
event_date <- current_venue$date_of_shoot
scores <- filter(archer_scores, event_date == shoot_date)
```

```{r}
club_scores <- function(theclub)
  tbl <- scores %>%
          filter(club == theclub) %>%
          arrange_at(c("score", "golds"), desc) %>%
          select(c("archer",  "score", "hits", "golds"))
```

*Venue:* `{r} venue_name`, `{r} town`

*Date:* `{r} event_date`

`{r} str_to_title(as.english(num_teams))` teams took part. The scores of the top four members of each time was summed, except for Strathclyde which had three archers, and Orion and Linwood, which had just one person on their team.

# Team Results

```{r}
team_results <- scores %>%
  select(c(club, score, hits, golds)) %>%
  group_by(club) %>%
  arrange_at(c("score", "golds"), desc) %>%
  slice_head(n=4) %>%
  summarise(across(everything(), sum)) %>%
  arrange_at(c("score", "golds"), desc)

knitr::kable(team_results, col.names = c("Club", "Score", "Hits", "Golds"))
```

# Individual Scores - by Bowstyle

### Ladies Recurve

```{r}
#| warning: false
lady_r <- score_table('Recurve', 'Ladies')
knitr::kable(lady_r, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Ladies Barebow

```{r}
lady_b <- score_table('Barebow', 'Ladies')
knitr::kable(lady_b, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Compound

```{r}
gent_c <- score_table('Compound', 'Gents')
knitr::kable(gent_c, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Recurve

```{r}
gent_r <- score_table('Recurve', 'Gents')
knitr::kable(gent_r, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Barebow

```{r}
gent_b <- score_table('Barebow', 'Gents')
knitr::kable(gent_b, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Longbow

```{r}
gent_l <- score_table('Longbow', 'Gents')
knitr::kable(gent_l, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

# Individual Scores - by Club

::: {.panel-tabset}
## Glasgow
```{r}
glas <- club_scores("Glasgow")
knitr::kable(glas, col.names = c("Archer", "Score", "Hits", "Golds"))
```

       
## East Kilbri
```{r}
ek <- club_scores("East Kilbride")
knitr::kable(ek, col.names = c("Archer", "Score", "Hits", "Golds"))
```

      
## Monklands
```{r}
monk <- club_scores("Monklands")
knitr::kable(monk, col.names = c("Archer", "Score", "Hits", "Golds"))
```

        
## Strathclyde
```{r}
strath <- club_scores("Strathclyde")
knitr::kable(strath, col.names = c("Archer", "Score", "Hits", "Golds"))
```

        
## Linwood
```{r}
lin <- club_scores("Linwood")
knitr::kable(lin, col.names = c("Archer", "Score", "Hits", "Golds"))
```

## Orion's
```{r}
orion <- club_scores("Orion's")
knitr::kable(orion, col.names = c("Archer", "Score", "Hits", "Golds"))
```

:::

