---
title: "East Kilbride January Tournament"
date: "2025-01-12"
execute: 
  echo: false
editor: visual
editor_options: 
  chunk_output_type: inline
---

```{r, install, eval=FALSE}
install.packages( "quarto", "tidyverse", "here", "english")
```

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 5)
library(tidyverse)
library(here)
library(english)
source(here("functions", "utility_functions.R"))
```

```{r}
event_date = ymd(20250112)
scores <- load_archers(event_date)
current_venue <- venue(event_date)
venue_name <- current_venue$location
town <- current_venue$town
num_teams <- n_distinct(scores$club)
```

*Venue:* `{r} venue_name`, `{r} town`

*Date:* `{r} event_date`

`{r} str_to_title(as.english(num_teams))` teams took part. The scores of the top four members of each time was summed, except Orion which had one archer, and Linwood, which had just three archers on their team.

# Team Results

```{r}
knitr::kable(team_results(scores), col.names = c("Club", "Score", "Hits", "Golds"))
```

# Individual Scores - by Bowstyle

### Ladies Recurve

```{r}
#| warning: false
lady_r <- score_table('Recurve', 'Ladies', scores)
knitr::kable(lady_r, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Ladies Barebow

```{r}
lady_b <- score_table('Barebow', 'Ladies', scores)
knitr::kable(lady_b, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Compound

```{r}
gent_c <- score_table('Compound', 'Gents', scores)
knitr::kable(gent_c, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Recurve

```{r}
gent_r <- score_table('Recurve', 'Gents', scores)
knitr::kable(gent_r, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Gents Barebow

```{r}
gent_b <- score_table('Barebow', 'Gents', scores)
knitr::kable(gent_b, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
```

### Ladies Traditional

```{r}
gent_t <- score_table('Traditional', 'Ladies', scores)
if (nrow(gent_t) > 0) {
    knitr::kable(gent_t, col.names = c("Archer", "Club", "Score", "Hits", "Golds"))
}
```

# Individual Scores - by Club

::: panel-tabset
## Glasgow

```{r}
glas <- club_scores("Glasgow", scores)
knitr::kable(glas, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## East Kilbride

```{r}
ek <- club_scores("East Kilbride", scores)
knitr::kable(ek, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Monklands

```{r}
monk <- club_scores("Monklands", scores)
knitr::kable(monk, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Strathclyde

```{r}
strath <- club_scores("Strathclyde", scores)
knitr::kable(strath, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```

## Linwood

```{r}
lin <- club_scores("Linwood", scores)
knitr::kable(lin, col.names = c("Archer", "Style", "Score", "Hits", "Golds"))
```
:::
